%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Copyright 2019
% Liturgy of St. John Chrysostom for regular Sundays
% Simple traditional Arabic chants through to the Trisagion,
% and then switching to more choral for the remainder of the service.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[twoside, letterpaper, 12pt]{report}
\usepackage{orthodoxservicebook}

\begin{document}
%\maketitle

\title{Divine Liturgy\\
As celebrated on most Sundays which are not Feast days}

\author{St. Katherine Orthodox Church}
\date{}% Remove date
\maketitle

\instruction{This page intentionally left blank}

\cleardoublepage
\chapter*{Divine Liturgy}
\centeredsection{Preparation and Opening Dialogue}

\begin{priest}
\item \input{Common/OheavenlyKing.txt}
\item Glory to God in the highest, and on earth peace, good will among men \instruction{2x}
\item O Lord, Thou shalt open my lips, and my mouth shall declare Thy praise.
\end{priest}

\deaconline{It is time for the Lord to act. Bless, father.}
\priestline{Blessed is our God, always, now and ever, and unto ages of ages.}
\deaconline{Amen. Pray for me, father.}
\priestline{The Lord direct thy steps unto every good work.}
\deaconline{Remember me, holy father.}
\priestline{The Lord God remember thee in His kingdom, always, now and ever, and unto ages of ages.}
\begin{deacon}
\item Amen.
\item O Lord, thou shalt open my lips, and my mouth shall declare Thy praise.
\item Bless, father
\end{deacon}

\instruction{This is proclaimed loudly, and signifies that preparations are complete,
  and the service is now beginning}
\priestline{Blessed is the kingdom of the Father and of the Son and of the Holy Spirit,
   now and ever and unto ages of ages.}

\lilypondfile{./Z-Responses/Kazan/Amen.ly}

% Want to ensure this pretty much starts on a new page.
\needspace{20\baselineskip}
\centeredsection{The Litany of Peace}

\deaconline{In peace, let us pray to the Lord.}
\instruction{Repeat these phrases until the last petition.}
\lilypondfile{./Z-Responses/Kazan/LordHaveMercy-A.ly}

\deaconline{For the peace from above and the salvation of our souls, let us pray to the Lord.}
\lilypondfile{./Z-Responses/Kazan/LordHaveMercy-B.ly}

\deaconline{For the peace of the whole world, the good estate of the holy churches of God
  and the union of all men, plet us pray to the Lord.}
\lilypondfile{./Z-Responses/Kazan/LordHaveMercy-C.ly}

\begin{deacon}
\item For this Holy House, and for those who with faith, reverence,
  and fear of God, enter therein,
  let us pray to the Lord.
\item For our father and Metropolitan N., (for our Archbishop N. or Bishop N.),
  for the venerable Priesthood, the Diaconate in Christ, for all the clergy and the people,
  let us pray to the Lord.
\item For the President of the United States, for all civil authorities,
  and for our Armed Forces everywhere, let us pray to the Lord.
\item For this city, and for every city and land, and for the faithful who dwell therein,
  let us pray to the Lord.
\item For healthful seasons, for abundance of the fruits of the earth, and for peaceful times,
  let us pray to the Lord.
\item For travelers by sea, by land, and by air; for the sick and the suffering;
  for captives and their salvation,
  let us pray to the Lord.
\item For our deliverance from all tribulation, wrath, danger, and necessity,
  let us pray to the Lord.
\item Help us; save us; have mercy on us; and keep us, O God, by Thy grace.
\end{deacon}
\lilypondfile{./Z-Responses/Kazan/LordHaveMercy-Z.ly}

\deaconline{Calling to remembrance our all-holy, immaculate, most blessed and glorious Lady the Theotokos\\
  \instruction{(Recited quietly as the petitioner continues)}\\
  \lilypondfile[staffsize=15]{./Z-Responses/Kazan/MostHolyTheotokosSaveUs.ly}\\
  and ever-virgin Mary, with all the Saints: let us commend ourselves and each other,
  and all our life unto Christ our God.
}

\lilypondfile{./Z-Responses/Kazan/ToTheeOLord.ly}

\priestline{For unto Thee are due all glory, honor, and worship:
  to the Father, and to the Son, and to the Holy Spirit; now and ever and unto ages of ages.}
\lilypondfile{./Z-Responses/Kazan/Amen.ly}

\centeredsection{The First Antiphon}
\lilypondfile{./Liturgy/B-FirstAntiphon/TheFirstAntiphon-Tone2SimpleByzChant-Music.ly}


\centeredsection{The Little Litany}
\deaconline{Again and again, in peace, let us pray to the Lord.}
\lilypondfile{./Z-Responses/Kazan/LordHaveMercy-A.ly}

\deaconline{Help us, save us, have mercy on us; and keep us, O God, by Thy grace.}
\lilypondfile{./Z-Responses/Kazan/LordHaveMercy-B.ly}

\needspace{5\baselineskip}
\deaconline{Calling to remembrance our all-holy, immaculate, most blessed and glorious Lady the Theotokos\\
  \instruction{(Recited quietly as the petitioner continues)}\\
  \lilypondfile[staffsize=15]{./Z-Responses/Kazan/MostHolyTheotokosSaveUs.ly}\\
  and ever-virgin Mary, with all the Saints: let us commend ourselves and each other,
  and all our life unto Christ our God.
}

\lilypondfile{./Z-Responses/Kazan/ToTheeOLord.ly}

\priestline{For Thine is the might, and Thine is the kingdom and the power and the glory
  of the Father and of the Son and of the Holy Spirit, now and ever, and unto ages of ages.}

\lilypondfile{./Z-Responses/Kazan/Amen.ly}

\centeredsection{The Second Antiphon}
\lilypondfile{./Liturgy/C-SecondAntiphon/TheSecondAntiphon-Tone2SimpleByzChant-Music.ly}
\needspace{10\baselineskip}
\lilypondfile{./Liturgy/C-SecondAntiphon/GNE-OnlyBegottenSon-Tone2SimpleByzChant-Music.ly}

\centeredsection{The Little Litany}
\deaconline{Again and again, in peace, let us pray to the Lord.}
\lilypondfile{./Z-Responses/Kazan/LordHaveMercy-A.ly}

\deaconline{Help us, save us, have mercy on us; and keep us, O God, by Thy grace.}
\lilypondfile{./Z-Responses/Kazan/LordHaveMercy-B.ly}

\needspace{5\baselineskip}
\deaconline{Calling to remembrance our all-holy, immaculate, most blessed and glorious Lady the Theotokos\\
  \instruction{(Recited quietly as the petitioner continues)}\\
  \lilypondfile[staffsize=15]{./Z-Responses/Kazan/MostHolyTheotokosSaveUs.ly}\\
  and ever-virgin Mary, with all the Saints: let us commend ourselves and each other,
  and all our life unto Christ our God.
}

\lilypondfile{./Z-Responses/Kazan/ToTheeOLord.ly}

\priestline{For Thou art a good God and lovest mankind,
  and unto thee we ascribe glory to the Father and to the Son and to the Holy Spirit,
  now and ever, and unto ages of ages.}
\lilypondfile{./Z-Responses/Kazan/Amen.ly}

\centeredsection{Apolytikion}
\instruction{Sing the Apolytikion appointed for the day as the 3rd antiphon before the entrance.}

\centeredsection{The Little Entrance}
\lilypondfile{./Liturgy/E-LittleEntrance/TheLittleEntrance-Tone2SimpleByzChant-Music.ly}

\centeredsection{Apolytikia}
\instruction{Again, sing the Apolytikia in the order appointed for the day.}

\cleardoublepage
\centeredsubsection{Apolytikion for Great-martyr Katherine the all-wise of Alexandria}
\instruction{On usual Sundays, one of the Apolytikia is that of the patron saint of the community}
\lilypondfile{./Menaion/11-25-StKatherine/Katherine-Trop_Tone5ByzChant-Music.ly}

\centeredsection{Kontakion}
\instruction{Sing the Kontakion in the order appointed for the day. }

\centeredsubsection{Kontakion to the Theotokos for Usual Sundays}
\instruction{On usual Sundays, the Kontakion is the `O Protection of Christians' hymn to the Theotokos}
\lilypondfile{./Liturgy/H-Kontakion/OProtectionOfChristians_Tone2ByzChant-Music.ly}

\cleardoublepage
\centeredsection{The Prayer of the Thrice-Holy Hymn}
\deaconline{Let us pray to the Lord}
\lilypondfile{./Z-Responses/Kazan/LordHaveMercy-A.ly}

\priestline{For holy art Thou, O our God, and unto Thee we ascribe glory
  to the Father and to the Son and to the Holy Spirit, now and ever...}
\deaconline{... and unto ages of ages.}

\lilypondfile{./Z-Responses/Moscow/Amen.ly}

\centeredsection{The Thrice-Holy Hymn}
\instruction{This may be replaced by the Baptismal or Hymn for the Cross as prescribed}
\vspace{12pt}
\lilypondfile{./Liturgy/I-ThriceHolyHymn/Trisagion_Arabic_a.ly}
\deaconline{With Strength.}
\lilypondfile{./Liturgy/I-ThriceHolyHymn/Trisagion_Arabic_b.ly}

\clearpage
\pagecolor{timberwolf}
\centeredsection{Anti-Trisagion Baptismal Hymn}
\instruction{Sung on certian days instead of the Thrice Holy Hymn}
\vspace{3pt}
\lilypondfile{./Liturgy/I-ThriceHolyHymn/AsManyAsHaveBeen-ByzPlain-a_Music.ly}
\deaconline{With Strength.}
\lilypondfile{./Liturgy/I-ThriceHolyHymn/AsManyAsHaveBeen-ByzPlain-b_Music.ly}
\clearpage
\nopagecolor


\centeredsection{The Readings from the New Testament}

\instruction{The appointed reader prepares to read the prokeimenon, facing the Royal Doors}

\deaconline{Let us attend}

\readerline{\instruction{Announces the prokeimenon of the epistle}}

\deaconline{Wisdom}

\readerline{\instruction{Announces the title of the epistle}}

\deaconline{Let us attend}

\readerline{\instruction{Turns to face the people and chants the appointed epistle}}

\priestline{Peace be to thee that readest}

\readerline{And to thy spirit. \instruction{Receives blessing
  and prepares to recite the alleluia verses while the choir sings:}}
\lilypondfile{./Liturgy/J-EpistleGospel/Alleluarion-A_Alaska-Music.ly}

\readerline{\instruction{Reads first Alleluia verse}}
\lilypondfile{./Liturgy/J-EpistleGospel/Alleluarion-B_Alaska-Music.ly}

\readerline{\instruction{Reads second Alleluia verse and returns to the congregation}}
\lilypondfile{./Liturgy/J-EpistleGospel/Alleluarion-C_Alaska-Music.ly}

\deaconline{Wisdom. Stand upright. Let us hear the holy gospel.}
\priestline{Peace be to all.}
\lilypondfile{./Z-Responses/Obikhod/AndToThySpirit.ly}

\deaconline{The reading from the holy gospel according to \instruction{N.}}
\lilypondfile{./Liturgy/J-EpistleGospel/GloryToThee_Obikhod-Music.ly}

\deaconline{Let us attend. \instruction{Chant the appointed lection}}

\lilypondfile{./Liturgy/J-EpistleGospel/GloryToThee_Obikhod-Music.ly}

\centeredsection{Homily}
\instruction{The priest replaces the gospel book upon the antiminsion and preaches the homily}

\cleardoublepage
\centeredsection{The Ektenia of Fervent Supplication}

\deaconline{Let us say with our whole soul and with our whole mind, let us say:}
\lilypondfile{./Z-Responses/Greek/PreThrefoldLhm_A.ly}

\deaconline{O Lord Almighty, the God of our fathers, we pray Thee hearken and have mercy.}
\lilypondfile{./Z-Responses/Greek/PreThrefoldLhm_B.ly}

\deaconline{Have mercy on us, O God, according to Thy great mercy,
    we pray Thee, hearken and have mercy.}
\instruction{The following is repeated for the remaining petitions}
\lilypondfile{./Z-Responses/Greek/LordHaveMercyX3.ly}

\begin{deacon}
\item Again we pray for all pious and Orthodox Christians.
\item Again we pray for our metropolitan (or archbishop),
  \instruction{N} and our bishop \instruction{N}.
\item Again we pray for our brethren: the priests, hieromonks, deacons,
  hierodeacons and monastics and all our brotherhood in Christ.
\item Again we pray for mercy, life, peace, health, salvation and visitation
  and pardon and forgiveness of sins for (the servants of God, \instruction{NN.}, and)
  all Orthodox Christians of true worship, who live and dwell in this community
\item Again we pray for the blessed and ever-memorable founders of this holy church
  (and for the servants of God, \instruction{NN.},) and all of our fathers and brethren,
  the Orthodox departed this life before us,
  who here and in all the world lie asleep in the Lord.
\item Again we pray for those who bear fruit and do good works in this holy
  and all-venerable temple,
  those who serve and those who sing and all the people here present,
  who await Thy great and rich mercy.
\end{deacon}

\begin{priest}
\item O Lord our God, receive this fervent supplication of Thy servants,
  and have mercy on us according to the multitude of Thy mercy,
  and send down Thy compassions upon us and upon all Thy people,
  who await Thy great and rich mercy.
\item For Thou art a merciful God and lovest mankind,
  and unto Thee we ascribe glory to the Father and to the Son and to the Holy Spirit,
  now and ever, and unto ages of ages.
\end{priest}

\lilypondfile{./Z-Responses/Obikhod/Amen.ly}


\centeredsection{The Litany for the Catechumens}
\instruction{The refrains are generally sung softly while the petitioner prays for the catechumens}
\deaconline{Pray to the Lord, ye catechumens.}
\lilypondfile{./Z-Responses/NKedrov/LordHaveMercyCatechumens_A.ly}

\deaconline{Let us, the faithful, pray for the catechumens,
  that the Lord will have mercy on them.}
\lilypondfile{./Z-Responses/NKedrov/LordHaveMercyCatechumens_B.ly}

\deaconline{That He will teach them the word of truth.}
\lilypondfile{./Z-Responses/NKedrov/LordHaveMercyCatechumens_C.ly}

\deaconline{That He will reveal to them the gospel of righteousness.}
\lilypondfile{./Z-Responses/NKedrov/LordHaveMercyCatechumens_D.ly}

\deaconline{That He will unite them to His holy, catholic and apostolic Church.}
\lilypondfile{./Z-Responses/NKedrov/LordHaveMercyCatechumens_E.ly}

\deaconline{Save them; have mercy on them; help them; and keep them, O God, by Thy grace.}
\lilypondfile{./Z-Responses/NKedrov/LordHaveMercyCatechumens_F.ly}

\deaconline{Bow your heads unto the Lord, ye catechumens.}
\lilypondfile{./Z-Responses/NKedrov/ToTheeOLord.ly}

\priestline{That with us they may glorify Thine all-honorable and majestic name of the Father
  and of the Son and of the Holy Spirit, now and ever, and of the Son and of the Holy Spirit,
  now and ever, and unto ages of ages.}
\lilypondfile{./Z-Responses/NKedrov/Amen.ly}


\centeredsection{The Liturgy of the Faithful}
\centeredsubsection{First Litany of the Faithful}

\deaconline{As many as are of the faithful, again and again in peace, let us pray to the Lord.}
\lilypondfile{./Z-Responses/NKedrov/LordHaveMercy_A.ly}

\deaconline{Help us; save us; have mercy upon us; and keep us, O God, by Thy grace.}
\lilypondfile{./Z-Responses/NKedrov/LordHaveMercy_B.ly}

\deaconline{Wisdom.}
\priestline{For unto Thee are due all glory, honor and worship to the Father and to the Son
  and to the Holy Spirit, now and ever, and unto ages of ages.}
\lilypondfile{./Z-Responses/NKedrov/Amen.ly}


\centeredsubsection{Second Litany of the Faithful}

\deaconline{Again and again in peace, let us pray to the Lord.}
\lilypondfile{./Z-Responses/NKedrov/LordHaveMercy_A.ly}

\deaconline{Help us; save us; have mercy upon us; and keep us, O God, by Thy grace.}
\lilypondfile{./Z-Responses/NKedrov/LordHaveMercy_B.ly}

\instruction{If a deacon is serving, they may intone four additional petitions.
  Repeat the refrains above for each}
\deaconline{Wisdom.}

\priestline{That gaurded always by Thy might we may ascribe glory unto Thee
  to the Father and to the Son and to the Holy spirit,
  now and ever, and unto ages of ages.}
\lilypondfile{./Z-Responses/NKedrov/Amen_B.ly}

\cleardoublepage
\centeredsubsection{The Chreubic Hymn}

\instruction{Tone 3}
\lilypondfile{./Liturgy/N-CherubicHymn/CherubicHymn_Gallatin-TwoPart-Music.ly}

\instruction{Harmonized}
\lilypondfile{./Liturgy/N-CherubicHymn/CherubicHymn_Gallatin-Harmonized-Music.ly}

\deaconline{All of you, the Lord God remember in His kingdom;
  always, now and ever, and unto ages of ages.}
\lilypondfile{./Z-Responses/Obikhod/Amen.ly}

\priestline{Our (Metropolitan or Archbishop or Bishop,) N.,
  and all our brotherhood in Christ, the Lord God remember in His Kingdom,
  always, now and ever, and unto ages of ages.}
\lilypondfile{./Z-Responses/Obikhod/Amen.ly}

\priestline{Our president, civil authorities and armed forces,
  the Lord God remember in his kingdom, always, now and ever, and unto ages of ages.}
\lilypondfile{./Z-Responses/Obikhod/Amen.ly}

\priestline{The Orthodox servant(s) of God, NN., that he(she, they) may have mercy,
  life, peace, salvation and visitation, pardon and forgiveness of sins,
  the Lord God remember in His kingdom, always, now and ever and unto ages of ages.}
\lilypondfile{./Z-Responses/Obikhod/Amen.ly}

\deaconline{The Orthodox servant(s) of God departed this life in the hope of the
  resurrection and life eternal, NN., the Lord God remember in His kingdom,
  always, now and ever, and unto ages of ages.}
\lilypondfile{./Liturgy/N-CherubicHymn/ThatWeMayReceive_Gallatin-Harmonized-Music.ly}


\cleardoublepage

\centeredsubsection{The Litany of Supplication}

\centeredsubsection{The Prayer of the Proskomedia}

\centeredsection{The Holy Anaphora}

\cleardoublepage
\centeredsubsection{Megalynarion}
\begin{priest}
\item That to those who shall partake therof they may be unto vigilance of soul,
  unto forgiveness of sins, unto the communion of Thy Holy Spirit,
  unto the fulfillment of the kingdom of heaven and unto boldness toward thee,
  not unto judgment nor unto condemnation.
  And again we offer unto thee this rational worship for all those who in faith
  have gone before us to their rest:
  forefathers, fathers, patriarchs, prophets, apostles, preachers, evangelists,
  martyrs, confessors, ascetics and every righteous spirit made perfect in faith:

\item Especially our all-holy, immaculate,
  most blessed and glorious Lady the Theotokos and ever-virgin Mary;
\end{priest}
\cleardoublepage

\centeredsection{The Lord's Prayer}

\centeredsection{Preparation of the Lamb}

\centeredsection{Pre-Communion Prayers}

\end{document}
