%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Copyright 2015
% This document, when compiled, produces the 6 psalms that are read at the
% beginning of Orthros (Matins), including the re-itteration of a phrase
% from the psalm after the psalm is completed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[twoside, twocolumn, 12pt]{report}
\usepackage{fancyhdr}
\pagestyle{fancy}
\setlength{\parindent}{0pt}

\begin{document}
%\maketitle
\newcommand{\mychapter}[2]{
	\setcounter{chapter}{#1}
	\setcounter{section}{0}
	\chapter*{#2}
	\addcontentsline{toc}{chapter}{#2}
}
\mychapter{0}{The Six Psalms for Orthros / Matins}
\texttt{\scriptsize The Orthros service begins with reflection and sobriety.
	As such, it is Antiochian practice to deliberately not cross
	oneself,
	intone the GNE, or make any movements from the beginning of the service,
	until the last psalm is read.}

\section*{Psalm 3}
\input{Psalm003.txt}

\mbox{}\\
%This line from the Psalm is repeated
I laid me down and slept; I awoke, for the Lord will help me.

\section*{Psalm 37}
\input{Psalm037.txt}

\mbox{}\\
%This line from the Psalm is repeated
Forsake me not, O Lord my God, depart not from me.
Be attentive unto my help, O Lord of my salvation.

\section*{Psalm 62}
\input{Psalm062.txt}

\mbox{}\\
%This line from the Psalm is repeated
At the dawn I meditated on Thee.
For Thou art become my helper;
in the shelter of Thy wings will I rejoice.
My soul hath cleaved after Thee;
Thy right hand hath been quick to help me.

\mbox{}\\
Glory to the Father, and to the Son,and to the Holy Spirit.
	Now and ever, and unto ages of ages. Amen.

\mbox{}\\
(Alleluia \texttt{3$\times$} Glory to Thee, O God.) \texttt{3$\times$} 

Lord, have mercy. \texttt{3$\times$}

\mbox{}\\
Glory to the Father, and to the Son, and to the Holy Spirit.

\texttt{\scriptsize Switch readers here, if desired.}

Now and ever, and unto ages of ages. Amen.

\section*{Psalm 87}
\input{Psalm087.txt}

\mbox{}\\
%This line from the Psalm is repeated
O Lord God of my salvation, by day have I cried and by night before Thee.
Let my prayer come before Thee, bow down Thine ear unto my supplication.

\section*{Psalm 102}
\input{Psalm102.txt}

\mbox{}\\
%This line from the Psalm is repeated
In every place of His dominion, bless the Lord, O my soul.

\section*{Psalm 142}
\input{Psalm142.txt}

\mbox{}\\
%This line from the Psalm is repeated
O Lord, give ear unto my supplication and enter not into judgment with Thy servant. \texttt{2$\times$}

\mbox{}\\
Thy good Spirit shall lead me in the land of uprightness.

\mbox{}\\
\texttt{\scriptsize The time of reflection is completed,
	so the conclusion is intoned.}

\emph{Glory to the Father, and to the Son,and to the Holy Spirit.
	Now and ever, and unto ages of ages. Amen.}

\mbox{}\\
\emph{(Alleluia \texttt{3$\times$} Glory to Thee, O God.) \texttt{3$\times$}}
	
\emph{O our God and our Hope, glory to Thee!}
\end{document}
