%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Copyright 2015
% This document contains all of the prayers that are said after partaking
% of holy communion. Generally by the reader while the congregation
% venerates the cross
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\emph{Priest: Glory to Thee, O God (3X)}

\section*{The Five Prayers}
\subsection*{Anonymous}
I thank Thee, O Lord my God,
that Thou hast not rejected me, a sinner,
but has vouchsafed me to become a communicant of Thy holy things.
I thank Thee that Thou hast vouchsafed me, the unworthy,
to partake of Thine immaculate and heavenly gifts.
But, O Master Who lovest mankind,
who didst both die for us and rise again and didst bestow
upon us these Thy dread and life-giving mysteries 
for the benefiting and sanctification of our souls and bodies:
Grant that they may be for me also unto healing of soul and body,
unto the averting of everything contrary thereto,
unto the enlightenment of the eyes of my heart,
unto the peace of my spiritual powers, unto faith unashamed,
unto love unfeigned, unto increase of wisdom,
unto the fulfillment of Thy commandments,
unto growth in Thy divine grace and the attainment of the kingdom,
that, preserved by them in Thy holiness,
I may ever remember Thy grace and henceforth live not unto myself,
but unto Thee, our Master and Benefactor.
And thus, when this life is ended in the hope of eternal life,
I may attain unto everlasting rest,
where the voice of those who keep festival is unceasing
and the delight of those who behold the ineffable beauty of Thy
countenance is boundless; 
for Thou art the true Desire and unutterable Joy of those 
who love Thee, O Christ our God, 
and all creation hymneth Thee forever. Amen.

\subsection*{A Prayer of Saint Basil the Great}
O Master, Christ our God, King of the ages and Maker of all things:
I thank Thee for all the good things that Thou hast bestowed upon me
and for this partaking of Thine immaculate and life-giving 
Mysteries. Wherefore, I pray Thee, Who art good and lovest mankind:
Keep me under thy protection and in the shadow of Thy wings;
and grant unto me with a pure conscience and even unto my last
breath to partake of Thy holy things unto forgiveness of sins
and unto life everlasting.
For Thou art the Bread of life, the Fountain of holiness,
the Giver of good things, and unto Thee we ascribe glory,
together with the Father and the Holy Spirit, now and ever,
and unto ages of ages. Amen.

\subsection*{A Prayer of Saint Simeon the Translator}
O Thou Who willingly dost give flesh to me as food,
Thou Who art a fire consuming the unworthy:
Consume me not, O my Creator, 
but rather pass through all my body parts, into all my joints,
my reins, my heart. Burn Thou the thorns of all my transgressions.
Cleanse my soul, and hallow Thou my thoughts.
Make firm my knees and my bones likewise.
Enlighten as one my five senses.
Establish me wholly in Thy fear. Ever shelter me, 
guard and keep me from every soul-corrupting deed and word.
Cleanse me, purify and control me. Adorn me, teach and enlighten me.
Show me to be a dwelling-place of Thy Spirit and in no wise
the dwelling-place of sin, that from me, Thy habitation,
through the entrance of Thy communion, 
every evil deed and every passion may flee as from fire.
As intercessors I bring to Thee all the sanctified,
both the leaders of the bodiless powers, the Forerunner
and Thy wise apostles and, besides these,
Thine immaculate and pure Mother. Do Thou receive our prayers,
O my Christ, Who art compassionate,
and make Thy servant to be a child of the light;
for Thou alone, O good One, art the Sanctification and Splendor
of our souls, and to Thee as God and Master, day by day,
we all ascribe glory.

\subsection*{Another Prayer}
May Thy holy Body, O Lord Jesus Christ our God, 
be unto me for life eternal, and thy precious Blood
unto forgiveness of my sins.
May this Eucharist be unto me for joy, health and gladness;
and at Thy fearful second coming make me,
the sinner, worthy to stand at the right hand of Thy glory,
through the intercessions of Thine all-immaculate Mother
and of all Thy saints. Amen.

\subsection*{A Prayer to the Most Holy Theotokos}
O all-holy Lady Theotokos, light of my darkened soul, my hope, 
my shelter, my refuge, my consolation and my joy:
I thank thee that thou hast accounted me worthy, although unworthy,
to be a partaker of the immaculate Body and precious Blood of Thy
Son. But do thou, who gavest birth to the true Light,
enlighten the spiritual eyes of my heart.
O thou who didst bear the Fountain of Immortality,
enliven thou me who lie dead in sin.
O compassion-loving Mother of the merciful God, have mercy on me,
and grant me humility and contrition of heart,
and humility in my thoughts and deliverance from the bondage
of my vain imaginings. And account me worthy,
even unto my last breath, to receive without condemnation
the sanctification of the immaculate Mysteries,
unto the healing of both soul and body.
And grant unto me tears of repentance and confession, 
that I may hymn thee and glorify thee all the days of my life,
for blessed and glorified art thou unto all ages. Amen.

\section*{Hymn of Simeon the God-receiver}
Lord, now lettest Thou Thy servant depart in peace, 
according to Thy word.
For mine eyes have seen Thy salvation,
which Thou hast prepared before the face of all people,
a light to lighten the Gentiles,
and the glory of Thy people Israel.

\section*{The Trisagion Prayers}
Holy God, Holy Mighty, Holy Immortal, have mercy on us. (3x)

\mbox{}\\
Glory to the Father, and to the Son, and to the Holy Spirit, both now and ever, and unto ages of ages. Amen.

\mbox{}\\
All-holy Trinity, have mercy on us.
Lord, cleanse us from our sins.
Master, pardon our iniquities.
Holy God, visit and heal our infirmities for Thy Name's sake.

\mbox{}\\
Lord, have mercy (x3)

\mbox{}\\
Glory to the Father, and to the Son, and to the Holy Spirit, both now and ever, and unto ages of ages. Amen.

\mbox{}\\
Our Father, Who art in heaven, hallowed by Thy Name;
Thy kingdom come; Thy will be done on earth as it is in heaven.
Give us this day our daily bread;
and forgive us our trespasses, as we forgive those who 
trespass against us.  And lead us not into temptation,
but deliver us from evil.

\mbox{}\\
\emph{Priest: For Thine is the kingdom, and the power, and the glory,
of the Father, and of the Son, and of the Holy Spirit, now and ever,
and unto ages of ages. Amen.}

\section*{Troparion of the Day}
\texttt{As assigned}

\section*{Troparion of the Patron (Saint Katherine)}
Let us praise the all-lauded and noble bride of Christ,
the godly Katherine,
the guardian of Sinai and its defense,
who is also our support and succor and our help;
for with the Holy Spirit's sword
she hath silenced brilliantly the clever among the godless;
and being crowned as a martyr, she now doth ask great mercy for us all.

\section*{Troparian and Kontakion}
\texttt{Only one of the following is read:}

\subsection*{A) Liturgy of St. John Chrysostom}
Grace shining forth from thy mouth like fire hath enlightened the universe
and hath disclosed to the world treasures of uncovetousness and hath shown
us the heights of humility.
But as thou dost instruct us by thy words,
O Father John Chrysostom, intercede with the Word,
Christ God, to save our souls.

\mbox{}\\
Glory to the Father and to the Son and to the Holy Spirit

\mbox{}\\
From heaven thou didst receive divine grace,
and by thy lips thou dost teach all to worship the one God in Trinity,
O venerable John Chrysostom,
the all-blessed.
Worthily do we extol thee,
for thou art an instructor that dost reveal things divine.

\subsection*{B) Liturgy of St. Basil the Great}
Thy sound hath gone out into all the earth, for it hath received thy word.
Thereby didst thou teach divine doctrine,
make clear the nature of existence,
and order the habits of men.
O thou of royal priesthood,
venerable Father Basil,
beseech Christ our God to grant us great mercy.

\mbox{}\\
Glory to the Father and to the Son and to the Holy Spirit

\mbox{}\\
Thou didst appear as an unshakable foundation of the Church,
dispensing an inviolate dominion to all mortals and sealing it with the
doctrines,
O revealer of heavenly things,
venerable Basil.

\section*{Doxology}

Both now and ever and unto ages of ages. Amen

\mbox{}\\
The Church is shown to be a many-lighted heaven that doth shine a guiding
light upon all them that do believe;
wherein while standing, we cry aloud:
Do thou thyself now establish this house, O Lord.

\mbox{}\\
Lord, have mercy. (12x)

\mbox{}\\
More honorable than the cherubim
and more glorious beyond compare than the seraphim,
thou who without corruption bearest God the Word,
and art truly Theotokos: We magnify thee.

\mbox{}\\
Bless, father, in the name of the Lord.

\mbox{}\\
\emph{Priest: May God have compassion upon us and bless us;
may he show the light of his countenance upon us and be merciful unto us.}

\mbox{}\\
Amen.

\mbox{}\\
\emph{Priest: Glory to thee,
O Christ our God and our Hope, glory to thee.}

\mbox{}\\
Glory to the Father and to the Son and unto the Holy Spirit
Both now and ever and unto ages of ages. Amen.

\mbox{}\\
Lord have mercy. (3x)

\mbox{}\\
Father, bless.

\mbox{}\\
\emph{Priest gives dismissal or simply ``Through the prayers...'')}

\mbox{}\\
Amen.
