% !TeX root = ../8-NinthHourSaturday.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Copyright 2019
% This document contains the ninth hour prayers layout as LaTeX commands.
% This allows the command to me modified depending on the day provided
% as an argument, (FUTURE) inserting the appropriate psalms for the day.
%
% The closing content is provided as a separate command, so that it can
% be optionally included.
%
% The TEX commands in this document require the orthodoxservicebook.sty
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\NinthHourContent}[1]{
\instruction{#1 - Plain Reading}
% TODO - Pull in the proper content based on the day of week argument

\priestline{Glory to Thee, O God \thrice}

\priestline{Blessed is our God always, now and ever, and unto ages of ages.}

\readerline{Amen.}

\instruction{Exclude from Pascha to Pentecost}
\begin{priest}
\item Glory to Thee, our God. Glory to Thee.
\item \input{./Common/OheavenlyKing.txt}
\end{priest}

\instruction{From Pascha to Ascension - CHANT
\emph{``Christ is risen from the dead, trampling down death by death,
and upon those in the tombs, bestowing life.''}
(3x), and then SKIP the first line
\emph{``Holy God, Holy Mighty, Holy Immortal: have mercy on us. \thrice''}}

\centeredsection{The Trisagion Prayers}
\input{./Common/TrisagionPrayerRecited-NeedsAmen.tex}

\begin{reader}
\item Amen.
\item Lord, have mercy. \twelve
\item Glory to the Father, and to the Son, and to the Holy Spirit;
  both now and ever, 
  and unto ages of ages. Amen.

\item O come, let us worship and fall down before God our King.\\
  O come, let us worship and fall down before Christ, our King and our God.\\
  O come, let us worship and fall down before the Very Christ, our King and our God.
\end{reader}
\begin{maybetwocolumns}
\squashedcenteredsection{Psalm 83} 
\input{./Psalms/Psalm083-unknwntrans.txt}

\squashedcenteredsection{Psalm 84}
\input{./Psalms/Psalm084-unknwntrans.txt}

\squashedcenteredsection{Psalm 85}
\input{./Psalms/Psalm085-unknwntrans.txt}

\needspace{2\baselineskip}
\instruction{And again:}

Work unto me a sign unto good, and let them that hate me behold and be put to shame;
for Thou, O Lord, hast holpen me and comforted me.

\end{maybetwocolumns}

\begin{reader}
  \item \gne
  \item Alleluia. Alleluia. Alleluia. Glory to Thee, O God. \thrice
  \item \lhmThree
  \item \glory
\end{reader}

\begin{maybetwocolumns}
\centeredsection{Apolytikion}
O ye apostles, martyrs and prophets, hierarchs,
venerable and righteous ones, who have 
finished well the contest and guarded the faith:
Beseech, we pray, since ye have boldness 
before the Savior who is good, that He may save our souls.

\readerline{\nowandever}

\centeredsection{Theotokion}

Thou who for our sake wast born of a virgin and didst suffer crucifixion,
O good One, 
and didst despoil death through death and as God didst reveal resurrection:
Despise not those whom Thou hast created with Thine own hand;
show forth Thy love for mankind,
O merciful One; accept the intercession of Thy mother, the Theotokos,
for us, and save Thy despairing people, O our Savior.

\vbox{}
Deliver us not up utterly, for Thy holy name’s sake,
neither disannul Thou Thy covenant, 
and cause not Thy mercy to depart from us,
for Abraham’s sake, Thy beloved,
and for Isaac’s sake, Thy servant,
and for Israel’s, Thy holy one.
\end{maybetwocolumns}

\centeredsection{Trisagion}
\input{Common/TrisagionPrayerRecited-NeedsAmen.tex}

\readerline{Amen.}

\begin{maybetwocolumns}
\instruction{Only one of the following:}

\centeredsection{(Not Lent) -- Kontakion}
\instruction{Outside of Lent}

Unto Thee, O Lord, the Author of creation, the universe doth offer the God-bearing
martyrs as the first-fruits of nature. By whose prayers, through the Theotokos,
do Thou preserve Thy Church in profound peace, O most merciful One.

\centeredsection{(Lent) -- Kontakion}
\instruction{During Lent}

When the thief beheld the Author of life hanging upon the cross, he said:
If Thou wert not God, who art here crucified with us,
then had the sun not veiled its rays,
neither would the earth have shaken with trembling.
But do Thou, who sufferest for all men, remember me,
O Lord, when Thou comest in Thy kingdom.

\vbox{}
Glory to the Father, and to the Son, and to the Holy Spirit.

\vbox{}
In the midst, between two thieves, was Thy cross found, the balance-beam of
righteousness; for while the one was led down to hades by the heaviness of his
blaspheming, the other was lightened of his sins,
unto the knowledge of things divine, O Christ God, glory to Thee.

\vbox{}
Both now and ever, and unto ages of ages. Amen.

\vbox{}
When she who bore Thee beheld upon the cross Thee, the Lamb and Shepherd and Savior
of the world, she weeping said: The world rejoiceth, in that it hath received redemption,
but my inward parts are inflamed as I behold Thy crucifixion, which Thou sufferest for all
men, O my Son and My God.

\centeredsection{Prayer of the Hours}
\readerline{\lhmForty}

Thou who, at all times and at every hour, both in heaven and on earth art
worshiped and glorified, O Christ God, long-suffering, plenteous in mercy
and compassion, who lovest the just and showest mercy to sinners, who callest
all men to salvation through the promise of good things to come: Do Thou, the
same Lord, receive also our supplications at this present hour, and direct our
lives according to Thy commandments. Sanctify our souls; purify our bodies;
set aright our minds; cleanse our thoughts; and deliver us from all calamity,
wrath and distress. Compass us round about with Thy holy Angels; that
guided and guarded by their hosts, we may attain unto the unity of the faith,
and unto the comprehension of Thine ineffable glory. For blessed art Thou unto
ages of ages. Amen.
\end{maybetwocolumns}

% if the end of maybetwocolumns is to close to the bottom,
% the below text may look like it's part of the first column instead of
% reverting back to full page.
\needspace{5\baselineskip}
\begin{reader}
\item \lhmThree
\item \gne
\item \input{Common/MoreHonorableThanTheCherubim.txt}
\item Bless, father in the name of the Lord.
\end{reader}

\priestline{May God have compassion upon us and bless us;
may He show the light of His countenance upon us and be merciful unto us.}

\readerline{Amen.}

\centeredsection{Prayer of St. Basil the Great}
\begin{maybetwocolumns}
O Master, Lord Jesus Christ our God, who art long-suffering toward our sins
and who hast led us even to the present hour, in which, as Thou didst hang
upon the life-giving tree Thou didst make a way into paradise for the penitent
thief and by death didst destroy death: Be gracious unto us sinners and Thine
unworthy servants; for we have sinned and dealt iniquitously, and we are not
worthy to lift up our eyes and look upon the heights of heaven, inasmuch as
we have departed from the path of Thy righteousness and have walked after the
desires of our own hearts. But we implore of Thy boundless goodness: Spare
us, O Lord, according to the multitude of Thy mercy, and save us, for Thy holy
name’s sake; for our days have passed away in vanity. Wrest us out of the
hand of the adversary, and forgive our sins, and mortify our carnal
imagination, that, putting off the old man, we may be clothed upon with the
new man and may live unto Thee, our Master and our Benefactor, and that, so
following after Thy commandments, we may attain unto rest eternal, where is
the abode of all those who rejoice. For Thou art, in verity, the true Joy and
Exultation of those who love Thee, O Christ our God, and unto Thee we ascribe
glory, together with Thine unoriginate Father and Thine all-holy and good and
life-giving Spirit, now and ever, and unto ages of ages. Amen.
\end{maybetwocolumns}
}

\newcommand{\NinthHourClosingContent}{
% This is omitted when Vespers follows immediately.
\priestline{Glory to Thee, O Christ our God and our Hope, glory to Thee.}

\begin{reader}
\item Glory to the Father and to the Son and to the Holy Spirit,
  both now and ever, and unto ages of ages. Amen.
\item \lhmThree
\item Father, bless.
\end{reader}

\begin{priest}
\item May Christ our true God,
  through the intercessions of His all-immaculate and all-blameless holy Mother;
  of the holy, glorious, and right-victorious martyrs;
  of our venerable and God-bearing fathers; of the holy and righteous ancestors
  of God, Joachim and Anna; of (N., saint of the day), whose memory we
  celebrate and of all the saints: have mercy upon us, and save us,
  forasmuch as He is good and loveth mankind.
\item Through the prayers of our holy fathers, Lord Jesus Christ our God,
  have mercy on us, and save us.
\end{priest}

\readerline{Amen.}
}
