%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Copyright 2015
% This document contains the ninth hour prayers,
% and depending on the day provided as an argument,
% inserts the appropriate psalms for the day.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\providecommand{\centeredsection}[1]{%
  \needspace{10\baselineskip}%
  \subsection*{\centering{}#1}%
}

\newcommand{\NinthHourContent}[1]{
\texttt{#1}
% TODO - Pull in the proper content based on the day of week argument
\texttt{Plain Reading}

\mbox{}\\
\emph{Priest: Glory to Thee, O God (3X)}

\mbox{}\\
\emph{Priest: Blessed is our God always, now and ever, and unto ages of ages.} 

\mbox{}\\
Reader: Amen.

\mbox{}\\

\texttt{Exclude from Pascha to Pentecost}

\emph{Priest:  
Glory to thee, our God. Glory to thee. O heavenly King, Comforter, the 
Spirit of truth, who art everywhere present and fill all things,
the Treasury of 
good things and Giver of life; Come, and abide in us and cleanse us from 
every stain and save our souls, O good One.}

\mbox{}\\
\texttt{Include from Pascha to Ascension}

Christ is risen from the dead, trampling down death by death, and upon those 
in the tomb, bestowing life. (3x) 

\mbox{}\\
\texttt{Exclude from Pascha to Ascension}

Holy God, Holy Mighty, Holy Immortal: have mercy on us. (3x) 

\mbox{}\\
\texttt{Start Here from Pascha to Ascension}

Glory to the Father, and to the Son,
and to the Holy Spirit; both now and ever, 
and unto ages of ages. Amen.

\mbox{}\\
All-holy Trinity, have mercy on us. Lord, cleanse us from our sins. Master, 
pardon our iniquities. Holy God, visit and heal our infirmities for Thy Name’s 
sake.

\mbox{}\\
Lord, have mercy. (3x)

\mbox{}\\
Glory to the Father, and to the Son, and to the Holy Spirit;
both now and ever, 
and unto ages of ages. Amen.

\mbox{}\\
Our Father, Who art in heaven, hallowed be Thy Name. Thy kingdom come; 
Thy will be done on earth as it is in heaven.
Give us this day our daily bread; 
and forgive us our trespasses,
as we forgive those who trespass against us, and 
lead us not into temptation, but deliver us from the evil one. 

\mbox{}\\
\emph{Priest: For Thine is the kingdom, and the power,
and the glory: of the Father, and of 
the Son, and of the Holy Spirit; now and ever, and unto ages of ages.}

\mbox{}\\
Amen.

\mbox{}\\
Lord, have mercy. (12x)

\mbox{}\\
Glory to the Father, and to the Son, and to the Holy Spirit;
both now and ever, 
and unto ages of ages. Amen.

\mbox{}\\ 
O come, let us worship and fall down before God our King. 
O come, let us worship and fall down before Christ, our King and our God. 
O come, let us worship and fall down before the Very Christ, our King and our 
God. 

\centeredsection{Psalm 83} 
How beloved are Thy dwellings, O Lord of hosts;
my soul longeth and fainteth for the 
courts of the Lord. 
My heart and my flesh have rejoiced in the living God. 
For the sparrow hath found herself a house,
and the turtledove a nest for herself where 
she may lay her young, 
Even Thine altars, O Lord of hosts, my King and my God. 
Blessed are they that dwell in Thy house;
unto ages of ages shall they praise Thee. 
Blessed is the man whose help is from Thee;
he hath made ascents in his heart, in the vale 
of weeping, in the place which he hath appointed. 
Yea, for the lawgiver will give blessings;
they shall go from strength to strength, the God 
of gods shall be seen in Sion. 
O Lord of hosts, hearken unto my prayer; give ear, O God of Jacob. 
O God, our defender, behold, and look upon the face of Thine anointed one. 
For better is one day in Thy courts than thousands elsewhere. 
I have chosen rather to be an outcast in the house of my God than to dwell in 
the tents of 
sinners. 
For the Lord loveth mercy and truth,
God will give grace and glory; the Lord will not 
withhold good things from them that walk in innocence. 
O Lord God of hosts, blessed is the man that hopeth in Thee. 

\centeredsection{Psalm 84}
Thou hast been gracious, O Lord, unto Thy land;
Thou hast turned back the captivity of 
Jacob. 
Thou hast forgiven the iniquities of Thy people,
Thou hast covered all their sins. 
Thou hast made all Thy wrath to cease,
Thou hast turned back from the wrath of Thine 
anger. 
Turn us back, O God of our salvation, and turn away Thine anger from us. 
Wilt Thou be wroth with us unto the ages? Or wilt Thou draw out Thy wrath from 
generation to generation? 
O God, Thou wilt turn and quicken us, and Thy people shall be glad in Thee. 
Show us, O Lord, Thy mercy, and Thy salvation do Thou give unto us. 
I will hear what the Lord God will speak in me;
for He will speak peace to His people 
and to His saints and to them that turn their heart unto Him. 
Surely nigh unto them that fear Him is His salvation,
that glory may dwell in our land. 
Mercy and truth are met together,
righteousness and peace have kissed each other. 
Truth is sprung up out of the earth,
and righteousness hath looked down from heaven. 
Yea, for the Lord will give goodness, and our land shall yield her fruit. 
Righteousness shall go before Him and shall set His footsteps in the way. 

\centeredsection{PSALM 85}
Bow down Thine ear, O Lord, and hearken unto me, for poor and needy am I. 
Preserve my soul, for I am holy;
save Thy servant, O my God, that hopeth in Thee. 
Have mercy on me, O Lord, for unto Thee will I cry all the day long;
make glad the soul 
of Thy servant, for unto Thee have I lifted up my soul. 
For Thou, O Lord, art good and gentle,
and plenteous in mercy unto all them that call 
upon Thee. 
Give ear, O Lord, unto my prayer,
and attend unto the voice of my supplication. 
In the day of mine affliction have I cried unto Thee, for Thou hast heard me. 
There is none like unto Thee among the gods, O Lord,
nor are there any works like unto 
Thy works. 
All the nations whom Thou hast made shall come and shall worship before Thee,
O Lord, 
and shall glorify Thy name. 
For Thou art great and workest wonders; Thou alone art God. 
Guide me, O Lord, in Thy way, and I will walk in Thy truth;
let my heart rejoice that I 
may fear Thy name. 
I will confess Thee, O Lord my God, with all my heart,
and I will glorify Thy name for ever. 
For great is Thy mercy upon me,
and Thou hast delivered my soul from the nethermost hades. 
O God, transgressors have risen up against me,
and the assembly of the mighty hath 
sought after my soul, and they have not set Thee before them. 
But Thou, O Lord my God, art compassionate and merciful,
long-suffering and plenteous in mercy, and true. 
Look upon me and have mercy upon me;
give Thy strength unto Thy servant, and save the son of Thy handmaiden. 
Work in me a sign unto good,
and let them that hate me behold and be put to shame;
for Thou, O Lord, hast holpen me and comforted me. 

\mbox{}\\
Glory to the Father, and to the Son, and to the Holy Spirit;
both now and ever, 
and unto ages of ages. Amen.

\mbox{}\\
Alleluia. Alleluia. Alleluia. Glory to thee, O God. (3x)

\mbox{}\\
Lord have mercy. (3x)

\centeredsection{Apolytikion}
Glory to the Father and to the Son and to the Holy Spirit.

\mbox{}\\ 
O ye apostles, martyrs and prophets, hierarchs,
venerable and righteous ones, who have 
finished well the contest and guarded the faith:
Beseech, we pray, since ye have boldness 
before the Savior who is good, that he may save our souls.
 
\centeredsection{Theotokion}
Both now and ever and unto ages of ages. Amen.

\mbox{}\\
Thou who for our sake wast born of a virgin and didst suffer crucifixion,
O good One, 
and didst despoil death through death and as God didst reveal resurrection:
Despise not those whom thou hast created with Thine own hand;
show forth Thy love for mankind,
O merciful One; accept the intercession of thy mother, the Theotokos,
for us, and save thy despairing people, O our Savior.
Deliver us not up utterly, for thy holy name’s sake,
neither disannul thou thy covenant, 
and cause not thy mercy to depart from us, for Abraham’s sake, thy beloved, and for Isaac’s sake, thy servant, and for Israel’s, thy holy one. 

\centeredsection{Trisagion}
Holy God, Holy Mighty, Holy Immortal: have mercy on us. (3x)

\mbox{}\\
Glory to the Father, and to the Son, and to the Holy Spirit;
both now and ever, 
and unto ages of ages. Amen.

\mbox{}\\
All-holy Trinity, have mercy on us. Lord, cleanse us from our sins. Master, 
pardon our iniquities.
Holy God, visit and heal our infirmities for Thy Name’s sake. 

\mbox{}\\
Lord, have mercy. (3x) 

\mbox{}\\
Glory to the Father, and to the Son, and to the Holy Spirit;
both now and ever,
and unto ages of ages. Amen. 

\mbox{}\\
Our Father, Who art in heaven, hallowed be Thy Name. Thy kingdom come; 
Thy will be done on earth as it is in heaven. Give us this day our daily bread; 
and forgive us our trespasses,
as we forgive those who trespass against us,
and lead us not into temptation,
but deliver us from the evil one.

\mbox{}\\
\emph{Priest: For Thine is the kingdom, and the power, and the glory:
of the Father, and of the Son, and of the Holy Spirit;
now and ever, and unto ages of ages.} 

Amen. 

\mbox{}\\
\texttt{Only one of the following:}

\centeredsection{A -- Kontakion}
\texttt{Outside of Lent}

Unto thee, O Lord, the Author of creation, the universe doth offer the God-bearing 
martyrs as the first-fruits of nature. By whose prayers, through the Theotokos, do Thou 
preserve in peace profound thy Church, O most merciful One. 



\centeredsection{B -- Kontakion}
\texttt{During Lent}

When the thief beheld the Author of life hanging upon the cross, he said:
If thou wert not god, who art here crucified with us,
then had the sun not veiled its rays,
neither would the earth have shaken with trembling.
But do thou, who sufferest for all men, remember me, 
O Lord, when thou comest in they kingdom. 
Glory to the Father, and to the Son, and to the Holy Spirit. 
In the midst, between two thieves, was thy cross found, the balance-beam of 
righteousness; for while the one was led down to hades by the heaviness of his 
blaspheming, the other was lightened of his sins, unto the knowledge of things divine, O 
Christ God, glory to thee. 
Both now and ever, and unto ages of ages. Amen. 
When she who bare thee beheld upon the cross thee, the Lamb and Shepherd and Savior 
of the world, she weeping said: The world rejoiceth, in that it hath received redemption, 
but my inward parts are inflamed as I behold thy crucifixion, which thou sufferest for all 
men, O my Son and My God.


\centeredsection{Prayer of the Hours}
Lord have mercy. (40x)

\mbox{}\\
Thou who, at all times and at every hour, both in heaven and on earth art 
worshipped and glorified, O Christ God, long-suffering, plenteous in mercy 
and compassion, who lovest the just and showest mercy to sinners, who callest 
all men to salvation through the promise of good things to come: Do Thou, the 
same Lord, receive also our supplications at this present hour, and direct our 
lives according to Thy commandments. Sanctify our souls; purify our bodies; 
set aright our minds; cleanse our thoughts; and deliver us from all calamity, 
wrath and distress. Compass us round about with Thy holy Angels; that 
guided and guarded by their hosts, we may attain unto the unity of the faith, 
and unto the comprehension of Thine ineffable glory. For blessed art thou unto 
ages of ages. Amen.

\mbox{}\\
Lord, have mercy. (3x)

\mbox{}\\
Glory to the Father, and to the Son, and to the Holy Spirit;
both now and ever, and unto ages of ages. Amen. 

\mbox{}\\
More honorable than the cherubim and more glorious beyond compare than 
the seraphim, thou who without corruption bearest God the Word and art truly 
Theotokos: We magnify thee.

\mbox{}\\
Bless, father in the name of the Lord. 

\mbox{}\\
\emph{Priest: May God have compassion upon us and bless us;
may he show the light of his countenance upon us and be merciful unto us.}

\mbox{}\\
Amen. 

\mbox{}\\
O Master, Lord Jesus Christ our God, who art long-suffering toward our sins 
and who hast led us even to the present hour, in which, as thou didst hang 
upon the life-giving tree thou didst make a way into paradise for the penitent 
thief and by death didst destroy death: Be gracious unto us sinners and thine 
unworthy servants; for we have sinned and dealt iniquitously, and we are not 
worthy to lift up our eyes and look upon the heights of heaven, inasmuch as 
we have departed from the path of thy righteousness and have walked after the 
desires of our own hearts. But we implore of thy boundless goodness: Spare 
us, O Lord, according to the multitude of thy mercy, and save us, for thy holy 
name’s sake; for our days have passed away in vanity. Wrest us out of the 
hand of the adversary, and forgive our sins, and mortify our carnal 
imagination, that, putting off the old man, we may be clothed upon with the 
new man and may live unto thee, our Master and our Benefactor, and that, so 
following after thy commandments, we may attain unto rest eternal, where is 
the abode of all those who rejoice. For Thou art, in verity, the true Joy and 
Exultation of those who love thee, O Christ our God, and unto thee we ascribe 
glory, together with thine unoriginate Father and thine all-holy and good and 
life-giving Spirit, now and ever, and unto ages of ages. Amen. 
}

\newcommand{\NinthHourClosingContent}{
% This is omitted when Vespers follows immediately.
\mbox{}\\
\emph {Priest: Glory to thee, O Christ our God and our Hope, glory to thee.}

\mbox{}\\
Reader: Glory to the Father and to the Son and to the Holy Spirit, both now and ever, 
and unto ages of ages. Amen.

\mbox{}\\
Lord, have mercy. (3x) 

\mbox{}\\
Father, bless.

\mbox{}\\
\emph{Priest: May Christ our true God,
through the intercessions of his all-immaculate and all-blameless holy Mother;
of the holy, glorious, and right-victorious martyrs; 
of our venerable and God-bearing fathers; of the holy and righteous ancestors 
of God Joachim and Anna; of (N., saint of the day), whose memory we 
celebrate, and of all the saints: have mercy upon us and save us forasmuch as 
he is good and loveth mankind. 
Through the prayers of our holy fathers, Lord Jesus Christ our God, have 
mercy on us, and save us.}

\mbox{}\\
Amen
}
